Online Verification of Commutativity

### 2020-09-08 acmPaper/paper.tex

There are several examples of reasonably complicated transformation graphs that we can pick from.  Gator includes several graphics examples as part of its examples package; for this evaluation, we looked at the \textit{phong}, \textit{reflection}, and \textit{shadow map} examples, sample images of which can be seen in Appendix~\ref{sec:gator-appendix}\xxx[as]{Either add text to appendix B or just reference a figure}.

We implemented a system for interfacing between the optimal set path checker (Algorithm 4) in the open-source implementation of Gator.
Using this algorithm, we found a bug in the reflection model, where a matrix was not being divided correctly by its determinant \xxx[dg]{List other things I find, if anything}\xxx[ak]{I think it may be nice to add more detail for at least one bug (code, what was the program doing, what the graph/conflict was, time taken, etc.)}.  We also inserted previous bugs to check the algorithm was working correctly, and it identified all inserted bugs\xxx[as]{This general observation is less interesting than specific bugs, and should be omitted to just use the specifics}.

>>>>

There are several examples of reasonably complicated transformation graphs that we can pick from.  Gator includes graphics examples as part of its examples package; for this evaluation, we looked at the \textit{phong}, \textit{reflection}, and \textit{shadow map} examples, sample images of which can be seen in Appendix~\ref{sec:gator-appendix}\xxx[as]{Either add text to appendix B or just reference a figure}.

We implemented a system for interfacing between the optimal set path checker (Algorithm 4) in the open-source implementation of Gator.
The system was tested with intentional bugs, of which it found them all, although no "real" bugs were found.  The graphs used were of size 5 or less; for graphs of this size, the checker was able to run in real time with no noticeable loss of frames.  Since the program is running at 60 frames per second, the checker was running at a rate faster than .01 seconds.
